Examination of shapes! (homework exam)

### 2016-02-27 geometricAlgorithms/homeworkExam/homeworkExam.tex
assignment I think I got the gits of it

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}

@@

\section{Polygon cut}
\section{Diagonal polygon cut}
\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}

@@

\section{Polygon cut}
Consider the following polygon:

\begin{tikzpicture}
	\draw (0,1.25) -- (2,1.25) -- (2,0) --
	 (1,1) -- (0,0) -- cycle;
\end{tikzpicture}

The best horizontal cut in this case is a cut that looks like so:

\begin{tikzpicture}
	\draw (0,1.25) -- (2,1.25) -- (2,0) --
	 (1,1) -- (0,0) -- cycle;
	 \draw [dotted] (0,1) -- (1,1);
\end{tikzpicture}

The reason for this is that the two triangles are bigger in area than
the connecting rectangle. But if we try to cut the entire figure we
end up with 3 different areas instead of 2. So the best cut we can
make will end up to  the depth of the trianlge enclave.

Now if you make the rectangle bigger something funny happens:

\begin{tikzpicture}
	\draw (0,2) -- (2,2) -- (2,0) --
	 (1,1) -- (0,0) -- cycle;
	 \draw [dotted] (0,1.25) -- (2,1.25);
\end{tikzpicture}

The best cut moves up to devide everything perfectly.
So we get an imperfect cut that *has* to end on a vertex according to
the lemma. Or we ge a perfect cut that may or may not end on a vertex.

\section{Diagonal polygon cut}
The most obvious solution is the brute force solution, which involves
having two loops that compare every possible cut from every vertex.
and just keep track of the best cut. this will take $O(n^2)$ time.
\end{document}
